### 2024-02-13 outputs/paper/paper.qmd
finished graph

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}
```{r}
file_path <- "../../outputs/data/bully_clean_data.csv"
bully_clean_data <- read.csv(file_path)
sample_data <- head(bully_clean_data, 6)
data<-bully_clean_data
```

Talk way more about it.

```{r}
data$MonthIndicator <- factor(data$Month, levels = month.abb)

# Regression to remove seasonal patterns and time trends
pre_process_model <- lm(logSearchst ~ as.factor(Year) + MonthIndicator, data = data)
data$logSearchst_star <- residuals(pre_process_model)

# Step 2: Month-by-Month Event Study Model
event_study_model <- lm(logSearchst_star ~ factor(Month, ordered = TRUE) + alphaPriorYearst + factor(State), data = data)

# Step 3: Nationwide Before-After Specification
before_after_model <- lm(logSearchst_star ~ factor(PostCOVID) + factor(State), data = data)

# Step 4: Time Period Analysis
time_period_model <- lm(logSearchst_star ~ factor(PostSpring) + factor(PostSummer) + factor(PostFall) + factor(State), data = data)

# Step 5: Differential Impact Analysis
differential_model <- lm(logSearchst_star ~ factor(PostSpring) + factor(PostSummer) + factor(PostFall) + factor(PostFall) * InPersons + factor(State), data = data)

# Additional Information
# Clustered standard errors
library(lmtest)
coeftest(event_study_model, vcov. = vcovHC(event_study_model, type = "HC1"))

# Weighted by population
weighted_model <- lm(logSearchst_star ~ factor(Month, ordered = TRUE) + alphaPriorYearst + factor(State), data = data, weights = your_population_weights)
```

# Results

```{r}
library(ggplot2)
library(dplyr)

# Assuming the date format is "%Y-%m-%d", you can use the following code
bully_data <- subset(bully_clean_data, bully_type == "bully")
bully_data <- bully_data %>%
  group_by(date) %>%
  summarise(Total = sum(num_of_searches))
schbully_data <- subset(bully_clean_data, bully_type == "schbully")
cyberbully_data <- subset(bully_clean_data, bully_type == "cyberbully")
# Create a ggplot object for the composite search measure
ggplot(bully_data, aes(x = date, y = Total)) +
  geom_point() +
  geom_segment(data = subset(bully_data, !is.na(lag(date))), aes(x = lag(date), y = lag(Total), xend = date, yend = Total), color = "blue") +
  ggtitle("Composite Search Intensity for School Bullying and Cyberbullying") +
  xlab("Date") +
  ylab("Logarithm of Nationwide Search Intensity (Relative to Jan 2016)") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), linetype = "dashed", color = "red")

# Create a ggplot object for School Bullying search intensity
ggplot(schbully_data, aes(x = date, y = num_of_searches)) +
  geom_point() +
  geom_line() +
  ggtitle("Search Intensity for School Bullying") +
  xlab("Date") +
  ylab("Logarithm of Nationwide Search Intensity (Relative to Jan 2016)") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), linetype = "dashed", color = "red")

# Create a ggplot object for Cyberbullying search intensity
ggplot(cyberbully_data, aes(x = date, y = num_of_searches)) +
  geom_point() +
  geom_line() +
  ggtitle("Search Intensity for Cyberbullying") +
  xlab("Date") +
  ylab("Logarithm of Nationwide Search Intensity (Relative to Jan 2016)") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), linetype = "dashed", color = "red")
```

```{r}
data <- data.frame(
  x = c(1, 2, 3, 4, 5),
  y = c(2, 4, 1, 6, 3)
)

# 指定要连接的点
connections <- data.frame(
  x1 = c(1, 2, 3, 4),
  y1 = c(2, 4, 1, 6),
  x2 = c(2, 3, 4, 5),
  y2 = c(4, 1, 6, 3)
)

# 使用ggplot函数创建图形
ggplot(data, aes(x = x, y = y)) +
  geom_point(color = "blue", size = 3) +
  geom_segment(data = connections, aes(x = x1, y = y1, xend = x2, yend = y2), color = "red") +
  labs(title = "点连接不同点的图", x = "X轴", y = "Y轴") +
  theme_minimal()
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

## Diagnostics

\newpage

# References

### 2024-02-13 scripts/01-download_data.R

@@ -22,17 +22,17 @@ library(opendatatoronto)
 # the raw data is in the /data/ folder in the replication package
 # change the file path to load the data into the project
 bullying_file_path <- 
-  "./inputs/data/2021_03_30_monthly_2012_2021_state_bullying_topic.csv"
+  "../inputs/data/2021_03_30_monthly_2012_2021_state_bullying_topic.csv"
 
 bullying_raw <- read.csv(bullying_file_path)
 
 cyberbully_file_path <-
-  "./inputs/data/2021_03_30_monthly_2012_2021_state_cyb_bullying_topic.csv"
+  "../inputs/data/2021_03_30_monthly_2012_2021_state_cyb_bullying_topic.csv"
 
 cyberbully_raw <- read.csv(cyberbully_file_path)
 
 schbully_file_path <-
-  "./inputs/data/2021_03_30_monthly_2012_2021_state_sch_bullying_topic.csv"
+  "../inputs/data/2021_03_30_monthly_2012_2021_state_sch_bullying_topic.csv"
 
 schbully_raw <- read.csv(schbully_file_path)
 
@@ -40,7 +40,7 @@ schbully_raw <- read.csv(schbully_file_path)
 #### Save data ####
 # [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(bullying_raw, "inputs/data/bullying_raw_data.csv") 
-write_csv(cyberbully_raw, "inputs/data/cyberbully_raw_data.csv") 
-write_csv(schbully_raw, "inputs/data/schbully_raw_data.csv") 
+write_csv(bullying_raw, "../inputs/data/bullying_raw_data.csv") 
+write_csv(cyberbully_raw, "../inputs/data/cyberbully_raw_data.csv") 
+write_csv(schbully_raw, "../inputs/data/schbully_raw_data.csv") 
 

### 2024-02-13 scripts/02-data_cleaning.R

@@ -18,9 +18,9 @@ library(tidyverse)
 
 #### Clean data ####
 # read in the raw data
-bullying_raw <- read.csv("inputs/data/bullying_raw_data.csv")
-cyberbully_raw <- read.csv("cyberbully_raw_data.csv")
-schbully_raw <- read.csv("schbully_raw_data.csv")
+bullying_raw <- read.csv("../inputs/data/bullying_raw_data.csv")
+cyberbully_raw <- read.csv("../inputs/data/cyberbully_raw_data.csv")
+schbully_raw <- read.csv("../inputs/data/schbully_raw_data.csv")
 
 # clean data
 # rename columns to improve readability
@@ -54,4 +54,5 @@ bully_comb_clean <- bind_rows(bully_comb, schbully_clean)
 
 
 #### Save data ####
-write_csv(bully_comb_clean, "outputs/data/bully_clean_data.csv")
+write_csv(bully_comb_clean, "../outputs/data/bully_clean_data.csv")
+

### 2024-02-14 outputs/paper/paper.qmd
graph done

@@
 bully_clean_data <- read.csv(file_path)
+bully_clean_data$date <- as.Date(bully_clean_data$date)
 sample_data <- head(bully_clean_data, 6)
-data<-bully_clean_data
 ```
@@
 Talk way more about it.
-
-```{r}
-data$MonthIndicator <- factor(data$Month, levels = month.abb)
-
-# Regression to remove seasonal patterns and time trends
-pre_process_model <- lm(logSearchst ~ as.factor(Year) + MonthIndicator, data = data)
-data$logSearchst_star <- residuals(pre_process_model)
-
-# Step 2: Month-by-Month Event Study Model
-event_study_model <- lm(logSearchst_star ~ factor(Month, ordered = TRUE) + alphaPriorYearst + factor(State), data = data)
-
-# Step 3: Nationwide Before-After Specification
-before_after_model <- lm(logSearchst_star ~ factor(PostCOVID) + factor(State), data = data)
-
-# Step 4: Time Period Analysis
-time_period_model <- lm(logSearchst_star ~ factor(PostSpring) + factor(PostSummer) + factor(PostFall) + factor(State), data = data)
-
-# Step 5: Differential Impact Analysis
-differential_model <- lm(logSearchst_star ~ factor(PostSpring) + factor(PostSummer) + factor(PostFall) + factor(PostFall) * InPersons + factor(State), data = data)
-
-# Additional Information
-# Clustered standard errors
-library(lmtest)
-coeftest(event_study_model, vcov. = vcovHC(event_study_model, type = "HC1"))
-
-# Weighted by population
-weighted_model <- lm(logSearchst_star ~ factor(Month, ordered = TRUE) + alphaPriorYearst + factor(State), data = data, weights = your_population_weights)
-```
 
@@
 library(dplyr)
+# Assuming the date format is "%Y-%m-%d", you can use the following code
+bully_data <- subset(bully_clean_data, bully_type == "sch_cyb_bully")
 
-# Assuming the date format is "%Y-%m-%d", you can use the following code
-bully_data <- subset(bully_clean_data, bully_type == "bully")
 bully_data <- bully_data %>%
@@
 schbully_data <- subset(bully_clean_data, bully_type == "schbully")
+schbully_data <- schbully_data %>%
+  group_by(date) %>%
+  summarise(Total = sum(num_of_searches))
 cyberbully_data <- subset(bully_clean_data, bully_type == "cyberbully")
+cyberbully_data <- cyberbully_data %>%
+  group_by(date) %>%
+  summarise(Total = sum(num_of_searches))
 # Create a ggplot object for the composite search measure
-ggplot(bully_data, aes(x = date, y = Total)) +
-  geom_point() +
-  geom_segment(data = subset(bully_data, !is.na(lag(date))), aes(x = lag(date), y = lag(Total), xend = date, yend = Total), color = "blue") +
+ggplot(bully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
+  geom_line() +
   ggtitle("Composite Search Intensity for School Bullying and Cyberbullying") +
   xlab("Date") +
-  ylab("Logarithm of Nationwide Search Intensity (Relative to Jan 2016)") +
-  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), linetype = "dashed", color = "red")
+  ylab("Search Intensity") +
+  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
+             linetype = "dashed", color = "red")+
+   scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
+               date_labels = "%Y-%m-%d", 
+               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-# Create a ggplot object for School Bullying search intensity
-ggplot(schbully_data, aes(x = date, y = num_of_searches)) +
-  geom_point() +
+ggplot(schbully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
   geom_line() +
-  ggtitle("Search Intensity for School Bullying") +
+  ggtitle("Composite Search Intensity for School Bullying") +
   xlab("Date") +
-  ylab("Logarithm of Nationwide Search Intensity (Relative to Jan 2016)") +
-  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), linetype = "dashed", color = "red")
+  ylab("Search Intensity") +
+  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
+             linetype = "dashed", color = "red")+
+  scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
+               date_labels = "%Y-%m-%d", 
+               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-# Create a ggplot object for Cyberbullying search intensity
-ggplot(cyberbully_data, aes(x = date, y = num_of_searches)) +
-  geom_point() +
+ggplot(cyberbully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
   geom_line() +
-  ggtitle("Search Intensity for Cyberbullying") +
+  ggtitle("Composite Search Intensity forCyberbullying") +
   xlab("Date") +
-  ylab("Logarithm of Nationwide Search Intensity (Relative to Jan 2016)") +
-  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), linetype = "dashed", color = "red")
-```
+  ylab("Search Intensity") +
+  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
+             linetype = "dashed", color = "red")+
+  scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
+               date_labels = "%Y-%m-%d", 
+               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
-```{r}
-data <- data.frame(
-  x = c(1, 2, 3, 4, 5),
-  y = c(2, 4, 1, 6, 3)
-)
-
-# 指定要连接的点
-connections <- data.frame(
-  x1 = c(1, 2, 3, 4),
-  y1 = c(2, 4, 1, 6),
-  x2 = c(2, 3, 4, 5),
-  y2 = c(4, 1, 6, 3)
-)
-
-# 使用ggplot函数创建图形
-ggplot(data, aes(x = x, y = y)) +
-  geom_point(color = "blue", size = 3) +
-  geom_segment(data = connections, aes(x = x1, y = y1, xend = x2, yend = y2), color = "red") +
-  labs(title = "点连接不同点的图", x = "X轴", y = "Y轴") +
-  theme_minimal()
 ```

### 2024-02-14 scripts/02-data_cleaning.R

@@ -18,15 +18,10 @@ library(tidyverse)
 
 #### Clean data ####
 # read in the raw data
-<<<<<<< HEAD
 bullying_raw <- read.csv("../inputs/data/bullying_raw_data.csv")
 cyberbully_raw <- read.csv("../inputs/data/cyberbully_raw_data.csv")
 schbully_raw <- read.csv("../inputs/data/schbully_raw_data.csv")
-=======
-bullying_raw <- read.csv("inputs/data/bullying_raw_data.csv")
-cyberbully_raw <- read.csv("inputs/data/cyberbully_raw_data.csv")
-schbully_raw <- read.csv("inputs/data/schbully_raw_data.csv")
->>>>>>> b8c7f12379b2918d551aeb67d2f09f971b8ae24f
+
 
 # clean data
 # rename columns to improve readability
@@ -60,9 +55,6 @@ bully_comb_clean <- bind_rows(bully_comb, schbully_clean)
 
 
 #### Save data ####
-<<<<<<< HEAD
 write_csv(bully_comb_clean, "../outputs/data/bully_clean_data.csv")
 
-=======
-write_csv(bully_comb_clean, "outputs/data/bully_clean_data.csv")
->>>>>>> b8c7f12379b2918d551aeb67d2f09f971b8ae24f
+

### 2024-02-15 outputs/paper/paper.qmd
update for adding data

@@
    scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
-               date_labels = "%Y-%m-%d", 
+               date_labels = "%Y-%m", 
                limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
@@
   scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
-               date_labels = "%Y-%m-%d", 
+               date_labels = "%Y-%m", 
                limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
@@
   scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
-               date_labels = "%Y-%m-%d", 
+               date_labels = "%Y-%m", 
                limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```
+
+```{r}
 

### 2024-02-15 scripts/02-data_cleaning.R
add data

@@ -21,13 +21,26 @@ library(tidyverse)
 bullying_raw <- read.csv("../inputs/data/bullying_raw_data.csv")
 cyberbully_raw <- read.csv("../inputs/data/cyberbully_raw_data.csv")
 schbully_raw <- read.csv("../inputs/data/schbully_raw_data.csv")
-
+pop_2019<- read.csv("../inputs/data/US_NY_Population_2019.csv")
+pop_2020<- read.csv("../inputs/data/US_NY_Population_2020.csv")
 
 # clean data
 # rename columns to improve readability
 # choose 3 states to investigate
 # add a column indicate the type of bullying
 # select the desired columns
+pop_2019_clean <-
+  pop_2019 |>
+  rename(Age = Age) |>
+  filter(Age %in% c("5-9", "10-14", "15-17")) |>
+  select(Age, Total)
+
+pop_2020_clean <-
+  pop_2020 |>
+  rename(Age = Age) |>
+  filter(Age %in% c("5-9", "10-14", "15-17")) |>
+  select(Age, Total)
+
 bully_clean <-
   bullying_raw |>
   rename(us_state = dma_json_code, num_of_searches = hits) |>

### 2024-02-15 outputs/paper/paper.qmd
adding

@@
 bully_clean_data$date <- as.Date(bully_clean_data$date)
+NY_pop_2019_clean<- read.csv("../../outputs/data/NY_pop_2019_clean.csv")
+NY_pop_2020_clean<- read.csv("../../outputs/data/NY_pop_2020_clean.csv")
+NJ_pop_2019_clean<- read.csv("../../outputs/data/NJ_pop_2019_clean.csv")
+NJ_pop_2020_clean<- read.csv("../../outputs/data/NJ_pop_2020_clean.csv")
+LA_pop_2019_clean<- read.csv("../../outputs/data/LA_pop_2019_clean.csv")
+LA_pop_2020_clean<- read.csv("../../outputs/data/LA_pop_2020_clean.csv")
 sample_data <- head(bully_clean_data, 6)
@@
 ```{r}
-
+data %>%
+  arrange(desc(pop)) %>%
+  mutate(country = factor(country)) %>%
+  ggplot(aes(x=gdpPercap, y=lifeExp, size = pop)) +
+    geom_point(alpha=0.5) +
+    scale_size(range = c(.1, 24), name="Population (M)")
 ```

### 2024-02-15 scripts/02-data_cleaning.R

@@ -21,26 +21,53 @@ library(tidyverse)
 bullying_raw <- read.csv("../inputs/data/bullying_raw_data.csv")
 cyberbully_raw <- read.csv("../inputs/data/cyberbully_raw_data.csv")
 schbully_raw <- read.csv("../inputs/data/schbully_raw_data.csv")
-pop_2019<- read.csv("../inputs/data/US_NY_Population_2019.csv")
-pop_2020<- read.csv("../inputs/data/US_NY_Population_2020.csv")
+LA_pop_2019<- read.csv("../inputs/data/US_LA_Population_2019.csv")
+LA_pop_2020<- read.csv("../inputs/data/US_LA_Population_2020.csv")
+NJ_pop_2019<- read.csv("../inputs/data/US_NJ_Population_2019.csv")
+NJ_pop_2020<- read.csv("../inputs/data/US_NJ_Population_2020.csv")
+NY_pop_2019<- read.csv("../inputs/data/US_NY_Population_2019.csv")
+NY_pop_2020<- read.csv("../inputs/data/US_NY_Population_2020.csv")
 
 # clean data
 # rename columns to improve readability
 # choose 3 states to investigate
 # add a column indicate the type of bullying
 # select the desired columns
-pop_2019_clean <-
+NY_pop_2019_clean <-
   pop_2019 |>
   rename(Age = Age) |>
   filter(Age %in% c("5-9", "10-14", "15-17")) |>
   select(Age, Total)
 
-pop_2020_clean <-
+NY_pop_2020_clean <-
   pop_2020 |>
   rename(Age = Age) |>
   filter(Age %in% c("5-9", "10-14", "15-17")) |>
   select(Age, Total)
 
+NJ_pop_2019_clean <-
+  pop_2019 |>
+  rename(Age = Age) |>
+  filter(Age %in% c("5-9", "10-14", "15-17")) |>
+  select(Age, Total)
+
+NJ_pop_2020_clean <-
+  pop_2020 |>
+  rename(Age = Age) |>
+  filter(Age %in% c("5-9", "10-14", "15-17")) |>
+  select(Age, Total)
+
+LA_pop_2019_clean <-
+  pop_2019 |>
+  rename(Age = Age) |>
+  filter(Age %in% c("5-9", "10-14", "15-17")) |>
+  select(Age, Total)
+
+LA_pop_2020_clean <-
+  pop_2020 |>
+  rename(Age = Age) |>
[…]

### 2024-02-15 outputs/paper/paper.qmd
finished result

--- 2024-02-15 outputs/paper/paper.qmd
@@
 bully_clean_data$date <- as.Date(bully_clean_data$date)
+pop_2019_clean<- read.csv("../../outputs/data/pop_2019_clean.csv")
+pop_2020_clean<- read.csv("../../outputs/data/pop_2020_clean.csv")
+state_ratios<- read.csv("../../outputs/data/state_ratios.csv")
 sample_data <- head(bully_clean_data, 6)
@@
 ```{r}
+#| label: fig-Composite-Search-Intensity
+#| fig-cap: Composite-Search-Intensity by type
+#| warning: false
+#| message: false
+#| echo: false
 library(ggplot2)
@@
 ```
+@fig-Composite-Search-Intensity shows the number of searches for bullying
+(by category) starting in 2012 and ending in 2021.
+The graph visually shows how bullying searches relate to time.
+From this we can see every year during the first month of school, the number of searches for bullying rises to a peak, and then quickly dwindles to a trough in the summer.
+Depending on where the red dotted line is, that's when the pandemic started.
+Affected by online learning, the search volume for bullying broke the pattern of previous years and remained at a low level.
+Only searches for cyberbullying rebounded, but not by much.
 
 ```{r}
-
+#| label: fig-Number-of-Searches-represented-by-point-size
+#| fig-cap: Composite-Search-Intensity by type
+#| warning: false
+#| message: false
+#| echo: false
+ggplot(data = state_ratios, aes(x = fraction, y = us_state, size = num_of_searches)) +
+  geom_point(alpha = 0.5, color = "blue") +  # Adjust color as needed
+  labs(title = "Scatter Plot of Fraction vs. US State",
+       x = "Fraction",
+       y = "US State",
+       subtitle = "Number of Searches represented by point size") +
+  theme_minimal()  # Customize the theme as needed
 ```

### 2024-02-15 scripts/02-data_cleaning.R

@@ -37,43 +37,68 @@ NY_pop_2019_clean <-
   pop_2019 |>
   rename(Age = Age) |>
   filter(Age %in% c("5-9", "10-14", "15-17")) |>
-  select(Age, Total)
+  mutate(state = 'NY') |>
+  select(Age, Total,state)
 
 NY_pop_2020_clean <-
   pop_2020 |>
   rename(Age = Age) |>
   filter(Age %in% c("5-9", "10-14", "15-17")) |>
-  select(Age, Total)
+  mutate(state = 'NY') |>
+  select(Age, Total,state)
 
 NJ_pop_2019_clean <-
   pop_2019 |>
   rename(Age = Age) |>
   filter(Age %in% c("5-9", "10-14", "15-17")) |>
-  select(Age, Total)
+  mutate(state = 'NJ') |>
+  select(Age, Total,state)
 
 NJ_pop_2020_clean <-
   pop_2020 |>
   rename(Age = Age) |>
   filter(Age %in% c("5-9", "10-14", "15-17")) |>
-  select(Age, Total)
+  mutate(state = 'NJ') |>
+  select(Age, Total,state)
 
 LA_pop_2019_clean <-
   pop_2019 |>
   rename(Age = Age) |>
   filter(Age %in% c("5-9", "10-14", "15-17")) |>
-  select(Age, Total)
+  mutate(state = 'LA') |>
+  select(Age, Total,state)
 
 LA_pop_2020_clean <-
   pop_2020 |>
   rename(Age = Age) |>
   filter(Age %in% c("5-9", "10-14", "15-17")) |>
-  select(Age, Total)
+  mutate(state = 'LA') |>
+  select(Age, Total,state)
+
+
+
+
+
 bully_clean <-
   bullying_raw |>
   rename(us_state = dma_json_code, num_of_searches = hits) |>
   filter(us_state %in% c("US-NY", "US-LA", "US-NJ")) |>
   mutate(bully_type = 'sch_cyb_bully') |>
   select(us_state, date, num_of_searches, bully_type)
+bully_with_US <-
+  bullying_raw |>
+  rename(us_state = dma_json_code, num_of_searches = hits) |>
+  filter(us_state %in% c("US-NY", "US-LA", "US-NJ","US")) |>
[…]

### 2024-02-15 outputs/paper/paper.qmd
add discussion

@@
 
-## First discussion point {#sec-first-point}
+## COVID-19 Effects on Bullying
+The overall bullying @fig-Composite-Search-Intensity displays a decreasing trend over time, with a significant decline when COVID-19 pandemic emerged.
+The impact of COVID-19 on bullying cases results in a reduction to the lowest levels observed.
+The search intensities of bullying during and after remote learning sometimes almost reached zero.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+It is clear that the incidence of school bullying has generally been decreasing over time.
+The original paper [cite] states that COVID-19 pandemic and remote learning has caused a decrease in school bullying cases.
+Our data has a slight different conclusion compared to the original paper[cite graph].
+It is observed that with the sudden COVID-19 outbreak in the United States around January 2020, instances of school bullying experienced a notable surge, almost reaching global maxima in February 2020.
+The unexpected rise in bullying during the pandemic could be attributed to various factors, for example, individuals seeking to alleviate stress through harmful behavior to other people.
+Furthermore, a disturbing trend of Chinese-hate emerged during this period, due to the misguided assumptions that China was responsible for spreading the virus [@citeChineseHate].
+Asian students, especially Chinese ethnicity, might experience discriminatory actions, verbal abuse, or physical assaults due to this misinformation.
+So it most likely contributed to an increase in school bullying cases.
+As schools closed down in February 2020, a consequential decline in bullying cases was observed, at times nearly reaching zero.
+This is understandable since student interactions have declined due to remote learning.
 
-## Second discussion point
+Surprisingly, the shift to remote learning during the COVID-19 pandemic did not lead to an expected increase in cyberbullying cases.
+Given that students spent the majority of their time on digital devices [@citeDigitalDevices], it was natural to assume that cyberbullying would increase.
+Instead, there was a noticeable decrease.
+This challenges the assumption about the relationship between online activity and cyberbullying.
+The reduction in personal interactions during remote learning may have played a role in diminishing students' motivations or reasons to engage in cyberbullying.
+Also, since students stayed at home, there would always be adult supervision, for students under 12 years old [@citeStudent], which may have regulated their behaviour.
+This indicates that face-to-face interactions and the environmental factors have a strong impact on the prevalence of online harassment.
+
+## Cyclic Pattern of Bullying During Semesters and Vacations
+In all three types of bullying (school bullying, cyber-bullying, and bullying), a cyclic pattern can be observed.
+It is clear that the data peaks during the months of January and September, which are the commencement of school terms, followed by a gradual reduction in bullying cases as the semester progresses.
+The local trough occurs during the summer vacation when students are away from school.
+It can be inferred that there might be a positive correlation between academic stress and bullying and between in-person interactions and bullying [@citeCorrelation].
+
+As the semester begins, students need to transition from a relaxed vacation state to a rigorous school learning state.
+As they navigate the challenges of academic demands, they may experience stress and peer pressure from many sources [@citePressure].
+This will urge students to release their emotions and stress by bullying other students.
+It is important for teachers and schools to see this trend and understand its implications.
+Effective strategies for mental health support should be carried out to deal with this, in order to reduce bullying.
+
+Furthermore, there is obviously a clear positive correlation between in-person interactions and incidents of bullying.
+During the semesters, students engage in regular face-to-face interactions, potentially creating opportunities for bullying to occur.
+During summer vacation and the Christmas holiday, students typically limit their interactions to family members, with occasional exceptions when hanging out with friends.
+This reduction in direct, in-person interactions tends to reduce social pressures.
+Some individuals may feel the need to show dominance within the school by performing bullying behaviors in the presence of others [@citeOthers].
+However, during vacations, the reduced personal interaction may reduce their need for such assertive actions, resulting in a decrease in bullying activities.
 
@@
 
-## Weaknesses and next steps
+## Limtations
+###
 
-Weaknesses and next steps should also be included.
+## Future Steps
 

### 2024-02-15 outputs/paper/paper.qmd
add limitation and future steps

@@
 ## COVID-19 Effects on Bullying
-The overall bullying @fig-Composite-Search-Intensity displays a decreasing trend over time, with a significant decline when COVID-19 pandemic emerged.
+The overall bullying (@fig-Composite-Search-Intensity) displays a decreasing trend over time, with a significant decline when COVID-19 pandemic emerged.
 The impact of COVID-19 on bullying cases results in a reduction to the lowest levels observed.
@@
 The original paper [cite] states that COVID-19 pandemic and remote learning has caused a decrease in school bullying cases.
-Our data has a slight different conclusion compared to the original paper[cite graph].
+Our data has a slight different conclusion compared to the original paper (@fig-Composite-Search-Intensity).
 It is observed that with the sudden COVID-19 outbreak in the United States around January 2020, instances of school bullying experienced a notable surge, almost reaching global maxima in February 2020.
@@
 ## Limtations
-###
+### Limited Comprehensive Representation
+One key limitation of the study is the relatively low number of data entries for each bullying type within each state, which are only 111 entries.
+This sample size may not be able to provide a comprehensive representation of the entire state.
+The analysis about bullying might be skewed.
+
+### Biases in Data Collection
+The paper has several biases in its data collection process.
+Firstly, it seems to lack consideration for various minority groups, such as those based on ethnicity, gender, or belonging to the LGBQT community.
+This could potentially cover up the bullying experiences faced by these groups, which limits the study's inclusivity.
+
+Additionally, socio-economic status is a critical factor influencing the bullying situation.
+Communities facing economic challenges lack sufficient teaching resources, and children might learn negative behaviors due to their challenging circumstances.
+However, the current dataset does not seem to account for these socio-economic factors, which should be added as a data feature.
+
+Moreover, the data collection method is conducted on Google Trends, which introduces another bias.
+People without access to a computer or Internet may not have their experiences included in the dataset.
+Unfortunately, these students, who face economic difficulties, are more likely to be targets of bullying.
+The data does not have their perspective which compromises the comprehensiveness of the study.
+Also, public data from Google Trends shows the trends in the search intensity.
+However, there is no information about the person who performed the search.
+It is hard to decide whether they are the victim, the bully, or a random person.
+
+### Time Inaccuracy
+The study analyzes the bullying situation before, during, and after COVID-19, specifically focuses on the impact of remote learning.
+Therefore, there are some limitations related to the temporal aspect of data collection.
+The closure of schools during the COVID-19 pandemic occurred on different dates across states.
+This difference in the timing of school closures introduces potential inaccuracy in the analysis.
 
 ## Future Steps
+Future research should focus on gathering more inclusive and representative data by increasing the volume of data entries and mitigating bias in data collection. 
+Beyond simply collecting data about bullying, researchers should investigate the mental well-being of students affected by bullying.By investigating their mental well-being, researchers can arrive at conclusions if the mental health support system is effective for students in the school.
+It is important to ensure that individuals who experience bullying have access to the necessary resources and support.
+This makes sure that the research not only analyzes the situation, but also contributes to actionable improvements for those affected.
 

### 2024-02-15 outputs/paper/paper.qmd
add features

@@
 # Introduction
+With pandemic outbreaks, most schools in the United States turned to online teaching models, and students moved from physical places with more social interaction to screens [@citeCovid19Effect].
+While the transition to virtual education has been accompanied by a variety of challenges, including academic setbacks and economic disparities, significant gaps remain in understanding the impact of virtual education on the social dynamics within schools.
+Most research has focused on education, i.e., whether this change to an online delivery model will affect student achievement.
+In this article, we will focus on a new aspect of the pandemic that is having a positive impact: school bullying.
 
-You can and should cross-reference sections and sub-sections.
-
-The remainder of this paper is structured as follows. @sec-data....
+Bullying in schools is pervasive and can have significant social costs.
+In the US, 1 in 5 students ages 12-18 has been bullied during the school year, and approximately 160,000 teens have skipped school because of bullying [@citeFacts].
+The COVID-19 pandemic has fundamentally changed the context of bullying dynamics.
+With the shift to online learning across the United States in March 2020, there is a sudden decrease in in-person communication and interaction while the use of technology increases dramatically.
+In fact, prior COVID-19 research has suggested that the higher the frequency of the Internet, the more incidents of cyberbullying and cyber-victimization reported by youth [@citeResearch].
+However, in this paper, we conclude that both school bullying and cyberbullying have been decreased during the pandemic by analyzing a long panel of publicly available Google Trends online search data.
+These results provide insights into how schools can reduce bullying in a post-pandemic world and highlight a possible mechanism by which COVID-19 may have a differential impact on broader mental health.
 
 # Data {#sec-data}
+
+## Data Source
+This paper will replicate the data that was originally collected for the paper “The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying” by [citation].
+Using the online platform “Google Trends”, which provide monthly internet search behavior for a given term or topic by states over a period of time, they collected three types of bullying data (“School Bullying”, “Cyberbullying”, and “Bullying”) before, during, and after the pandemic COVID-19 from January 2012 to February 2021.
+They filtered the data to keep male and female individuals between ages of 5 and 17 (roughly the k-12 schooling population).
+Each dataset contains 5661 rows and 5 variables, each indicating a detailed summary of the month and position of the search, search keyword, number of searches and the ratio.
+
+The researchers state that data from Google Trends are less likely to be subjected to potential bias, since the data are not self-reported.
+Moreover, the data from Google Trends represents the full population of Google search users in the United States, thus it does not have the potential issue of under-representation of a certain group.
+
+## Methodology
+Since it is difficult to observe through 16683 (5661*3) rows with 5 variables, this report will only observe and analyze through specific aspects.
+The original dataset contains information through all the 51 states in the US.
+This paper focuses only on data and trends for three states, which are “US-LA”, “US-NY” and “US-NJ” (Louisiana, New York, and New Jersey respectively).
+Some data cleaning is performed, such as renaming column names, filtering and mutating the column, etc.
+The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `knitr` (@citeKnitr), `dplyr` (@citeDplyr), `ggplot2` (@citeGgplot2).
+
+## Features
+The original dataset contained 5 variables, which are named as “dma_json_code”, “date”, “keyword”, “hits”, and “ratio”. 
+1. dma_json_code: the states of the United States
+2. date: the first day of every month from 2012. 01 to 2021. 02
+3. keyword: specific words that the people search on Google Trends that relate to bullying.
+4. hits: number of searchers of keywords in each month.
+5. ratio:
+
 ```{r}
@@
 This is understandable since student interactions have declined due to remote learning.
+They did not have  as much opportunity or motivation to bully others as they had before.
 

### 2024-02-15 outputs/paper/paper.qmd
small fix

@@
 
+# install packages
 library(tidyverse)
@@
 ```{r}
+#| warning: false
+#| message: false
+#| echo: false
+
+# import cleaned data
 file_path <- "../../outputs/data/bully_clean_data.csv"
@@
 #| echo: false
+
+# plot graphs
 library(ggplot2)
 library(dplyr)
-# Assuming the date format is "%Y-%m-%d", you can use the following code
+
 bully_data <- subset(bully_clean_data, bully_type == "sch_cyb_bully")
@@
   summarise(Total = sum(num_of_searches))
-# Create a ggplot object for the composite search measure
+
+# plot from "bullying" data
 ggplot(bully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
@@
 
+# plot from "school bullying" data
 ggplot(schbully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
@@
 
+# plot from "cyberbullying" data
 ggplot(cyberbully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
@@
 #| echo: false
+
 ggplot(data = state_ratios, aes(x = fraction, y = us_state, size = num_of_searches)) +

### 2024-02-15 outputs/paper/paper.qmd
add discussion point 3

@@
 
-## Third discussion point
+## Regional Dynamics in Bullying Patterns
+The bullying searches show some regional variations, with New York state having the highest number of bullying searches.
+This could be due to New York's large population and the heightened personal physical interactions.
+The busy and dynamic environment of New York may contribute to increased stress for everyone, from various sources such as work, school, societal judgments, and economic pressures.
+All these pressures may induce bullying behaviours to happen.
+Also, the city's frequent occurrences of violent incidents might also potentially influence some students to engage in bullying behaviors.
+
+On the other hand, states like New Jersey (NJ) and Louisiana (LA) report fewer bullying cases.
+These states may have less intense environments, potentially resulting in decreased stress, hence less bullying to happen.
+
+It is apparent that different regions have different effects on bullying.
+Considering the physical environment students find themselves in, it can significantly impact their decisions to engage in bullying or not.
+External factors have strong influences on students’ judgments and behaviors.
+Therefore, it is important to have different measures to prevent bullying in different states to better address this issue.
 

### 2024-02-15 outputs/paper/paper.qmd
change paper layout and corss-ref

--- 2024-02-15 outputs/paper/paper.qmd
@@
 # install packages
+# install.packages("tidyverse)
+# install.packages("ggplot2)
+# install.packages("dplyr)
+
 library(tidyverse)
-library(palmerpenguins)
+library(ggplot2)
+library(dplyr)
 ```
@@
 Some data cleaning is performed, such as renaming column names, filtering and mutating the column, etc.
-The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `knitr` (@citeKnitr), `dplyr` (@citeDplyr), `ggplot2` (@citeGgplot2).
+The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `dplyr` (@citeDplyr), `ggplot2` (@citeGgplot2).
 
@@
 #| echo: false
-
 # import cleaned data
@@
 ```{r}
-#| label: fig-Composite-Search-Intensity
-#| fig-cap: Composite-Search-Intensity by type
+#| label: fig-Composite-Search-Intensity-bully
+#| fig-cap: Composite-Search-Intensity by School Bullying and Cyber Bullying
 #| warning: false
@@
 # plot graphs
-library(ggplot2)
-library(dplyr)
-
 bully_data <- subset(bully_clean_data, bully_type == "sch_cyb_bully")
@@
   geom_line() +
-  ggtitle("Composite Search Intensity for School Bullying and Cyberbullying") +
   xlab("Date") +
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+```{r}
+#| label: fig-Composite-Search-Intensity-sch
+#| fig-cap: Composite-Search-Intensity by School Bullying
+#| warning: false
+#| message: false
+#| echo: false
 
@@
   geom_line() +
-  ggtitle("Composite Search Intensity for School Bullying") +
   xlab("Date") +
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+```{r}
+#| label: fig-Composite-Search-Intensity-cyber
+#| fig-cap: Composite-Search-Intensity by Cyber Bullying
+#| warning: false
+#| message: false
+#| echo: false
 
@@
   geom_line() +
-  ggtitle("Composite Search Intensity forCyberbullying") +
   xlab("Date") +
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
 ```
-@fig-Composite-Search-Intensity shows the number of searches for bullying
+@fig-Composite-Search-Intensity-bully, @fig-Composite-Search-Intensity-sch, @fig-Composite-Search-Intensity-cyber shows the number of searches for bullying
 (by category) starting in 2012 and ending in 2021.
@@
 
+\newpage
+
 # Discussion
@@
 ## COVID-19 Effects on Bullying
-The overall bullying (@fig-Composite-Search-Intensity) displays a decreasing trend over time, with a significant decline when COVID-19 pandemic emerged.
+The overall bullying (@fig-Composite-Search-Intensity-bully) displays a decreasing trend over time, with a significant decline when COVID-19 pandemic emerged.
 The impact of COVID-19 on bullying cases results in a reduction to the lowest levels observed.
@@
 The original paper [cite] states that COVID-19 pandemic and remote learning has caused a decrease in school bullying cases.
-Our data has a slight different conclusion compared to the original paper (@fig-Composite-Search-Intensity).
+Our data has a slight different conclusion compared to the original paper (@fig-Composite-Search-Intensity-bully).
 It is observed that with the sudden COVID-19 outbreak in the United States around January 2020, instances of school bullying experienced a notable surge, almost reaching global maxima in February 2020.

### 2024-02-15 outputs/paper/paper.qmd
result adding

--- 2024-02-15 outputs/paper/paper.qmd
@@
 #| label: fig-Composite-Search-Intensity 
-#| fig-cap: Composite-Search-Intensity by type
+#| fig-cap: Composite-Search-Intensity both type
 #| warning: false
@@
 
+```
+
+```{r}
+#| label: fig-Composite-Search-Intensity-school
+#| fig-cap: Composite-Search-Intensity school type
+#| warning: false
+#| message: false
+#| echo: false
 # plot from "school bullying" data
@@
 
+```
+
+```{r}
+#| label: fig-Composite-Search-Intensity-cyber
+#| fig-cap: Composite-Search-Intensity cyber type
+#| warning: false
+#| message: false
+#| echo: false
 # plot from "cyberbullying" data
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
 
-```
-@fig-Composite-Search-Intensity shows the number of searches for bullying
-(by category) starting in 2012 and ending in 2021.
-The graph visually shows how bullying searches relate to time.
-From this we can see every year during the first month of school, the number of searches for bullying rises to a peak, and then quickly dwindles to a trough in the summer.
-Depending on where the red dotted line is, that's when the pandemic started.
-Affected by online learning, the search volume for bullying broke the pattern of previous years and remained at a low level.
-Only searches for cyberbullying rebounded, but not by much.
+ The data presented in @fig-Composite-Search-Intensity provides valuable insights into the trends of searches from 2012 to 2021.
+The observed pattern, with peaks of bullying during the first month of school and troughs in the summer, suggests a recurring seasonal variation in the interest or concern about bullying .
+This cyclic behavior aligns with the typical school calendar, highlighting a potential correlation between the academic year's start and increased awareness or experiences related to bullying.
+
+The introduction of the red dotted line indicating the onset of the pandemic adds an intriguing layer to the analysis.
+It appears that the traditional pattern of increased bullying searches during the initial school month was disrupted by the pandemic.(@fig-Composite-Search-Intensity-school ) With the shift to online learning, there was a noticeable departure from the usual surge in bullying-related searches.
+This alteration in behavior might be attributed to changes in the educational environment, as students and educators adapted to new modes of interaction.
+
+Surprisingly, despite the overall decrease in bullying searches during the pandemic, cyberbullying searches saw a notable rebound.(@fig-Composite-Search-Intensity-cyber ) This suggests that while traditional forms of bullying may have diminished due to reduced in-person interactions, the online realm became a focal point for bullying concerns.
+The fact that cyberbullying searches did not rebound significantly may indicate that, even in the digital space, the overall awareness or concerns related to bullying remained somewhat subdued during this period.
+
+The findings underscore the complex interplay between societal factors, educational settings, and the digital landscape in shaping the dynamics of bullying searches.
+Future research could delve deeper into the specific nuances of cyberbullying during the pandemic, exploring how the online learning environment may have influenced the prevalence and perception of such incidents.
+Additionally, understanding the lasting impact of these changes on bullying awareness and intervention efforts is crucial for developing effective strategies to address this issue in evolving educational landscapes.
 

### 2024-02-15 outputs/paper/paper.qmd
add and change structure and ref

--- 2024-02-15 outputs/paper/paper.qmd
@@
 
+This paper is structured as follows.
+In @sec-data, the sources of the data sets in the original paper, the methodologies used to collect them, and data features are explained.
+In @sec-result, a replication of the original study is conducted to analyze its findings and produce visual representations that enhances the analysis.
+In @sec-discussion, discussions are conducted based on the findings, which addresses the influence of COVID-19 pandemic on bullying, the cyclic pattern of bullying, regional pattern of bullying, limitation and future steps of this study.
+
 # Data {#sec-data}
@@
 ## Data Source
-This paper will replicate the data that was originally collected for the paper “The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying” by [citation].
+This paper will replicate the data that was originally collected for the paper “The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying” by @citePaper.
 Using the online platform “Google Trends”, which provide monthly internet search behavior for a given term or topic by states over a period of time, they collected three types of bullying data (“School Bullying”, “Cyberbullying”, and “Bullying”) before, during, and after the pandemic COVID-19 from January 2012 to February 2021.
@@
 #| echo: false
+
 # import cleaned data
@@
 
-# Results
+# Results {#sec-result}
 
@@
 #| echo: false
-
 # plot from "school bullying" data
@@
 ```
-@fig-Composite-Search-Intensity-bully, @fig-Composite-Search-Intensity-sch, @fig-Composite-Search-Intensity-cyber shows the number of searches for bullying
-(by category) starting in 2012 and ending in 2021.
-The graph visually shows how bullying searches relate to time.
-From this we can see every year during the first month of school, the number of searches for bullying rises to a peak, and then quickly dwindles to a trough in the summer.
-Depending on where the red dotted line is, that's when the pandemic started.
-Affected by online learning, the search volume for bullying broke the pattern of previous years and remained at a low level.
-Only searches for cyberbullying rebounded, but not by much.
+
+ The data presented in @fig-Composite-Search-Intensity-bully provides valuable insights into the trends of searches from 2012 to 2021.
+The observed pattern, with peaks of bullying during the first month of school and troughs in the summer, suggests a recurring seasonal variation in the interest or concern about bullying .
+This cyclic behavior aligns with the typical school calendar, highlighting a potential correlation between the academic year's start and increased awareness or experiences related to bullying.
+
+The introduction of the red dotted line indicating the onset of the pandemic adds an intriguing layer to the analysis.
+It appears that the traditional pattern of increased bullying searches during the initial school month was disrupted by the pandemic.
+In @fig-Composite-Search-Intensity-sch, we can see that with the shift to online learning, there was a noticeable departure from the usual surge in bullying-related searches.
+This alteration in behavior might be attributed to changes in the educational environment, as students and educators adapted to new modes of interaction.
+
+Surprisingly, despite the overall decrease in bullying searches during the pandemic, cyberbullying searches saw a notable rebound.
+(@fig-Composite-Search-Intensity-cyber) This suggests that while traditional forms of bullying may have diminished due to reduced in-person interactions, the online realm became a focal point for bullying concerns.
+The fact that cyberbullying searches did not rebound significantly may indicate that, even in the digital space, the overall awareness or concerns related to bullying remained somewhat subdued during this period.
+
+The findings underscore the complex interplay between societal factors, educational settings, and the digital landscape in shaping the dynamics of bullying searches.
+Future research could delve deeper into the specific nuances of cyberbullying during the pandemic, exploring how the online learning environment may have influenced the prevalence and perception of such incidents.
+Additionally, understanding the lasting impact of these changes on bullying awareness and intervention efforts is crucial for developing effective strategies to address this issue in evolving educational landscapes.
 
@@
 #| label: fig-Number-of-Searches-represented-by-point-size
-#| fig-cap: Composite-Search-Intensity by type
+#| fig-cap: Scatter Plot of Fraction vs. US State, number of searches represented by point size
 #| warning: false
@@
   geom_point(alpha = 0.5, color = "blue") +  # Adjust color as needed
-  labs(title = "Scatter Plot of Fraction vs. US State",
-       x = "Fraction",
-       y = "US State",
-       subtitle = "Number of Searches represented by point size") +
+  labs(x = "Fraction", y = "US State") +
   theme_minimal()  # Customize the theme as needed
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 

### 2024-02-15 outputs/paper/paper.qmd

@@
 # Introduction
-With pandemic outbreaks, most schools in the United States turned to online teaching models, and students moved from physical places with more social interaction to screens [@citeCovid19Effect].
+With pandemic outbreaks, most schools in the United States turned to online teaching models, and students moved from physical places with more social interaction to screens (@citeCovid19Effect).
 While the transition to virtual education has been accompanied by a variety of challenges, including academic setbacks and economic disparities, significant gaps remain in understanding the impact of virtual education on the social dynamics within schools.
@@
 Bullying in schools is pervasive and can have significant social costs.
-In the US, 1 in 5 students ages 12-18 has been bullied during the school year, and approximately 160,000 teens have skipped school because of bullying [@citeFacts].
+In the US, 1 in 5 students ages 12-18 has been bullied during the school year, and approximately 160,000 teens have skipped school because of bullying (@citeFacts).
 The COVID-19 pandemic has fundamentally changed the context of bullying dynamics.
 With the shift to online learning across the United States in March 2020, there is a sudden decrease in in-person communication and interaction while the use of technology increases dramatically.
-In fact, prior COVID-19 research has suggested that the higher the frequency of the Internet, the more incidents of cyberbullying and cyber-victimization reported by youth [@citeResearch].
+In fact, prior COVID-19 research has suggested that the higher the frequency of the Internet, the more incidents of cyberbullying and cyber-victimization reported by youth (@citeResearch).
 However, in this paper, we conclude that both school bullying and cyberbullying have been decreased during the pandemic by analyzing a long panel of publicly available Google Trends online search data.
@@
 Moreover, the data from Google Trends represents the full population of Google search users in the United States, thus it does not have the potential issue of under-representation of a certain group.
+
+## Data Measurements
+The measurement of bullying from Google Trends is the search intensity of keywords, which are published every month [@citePaper].
+Search intensity stands for the fraction of a given area’s Google searches for a specific topic.
+Google Trends normalizes the search intensity numbers to get relative intensity over time and across states.
+The search intensity is measured on a scale of 0 to 100, where 0 represents the lowest search intensity and 100 the highest.
 
@@
 ```
-
-Talk way more about it.
 
@@
 It is clear that the incidence of school bullying has generally been decreasing over time.
-The original paper [cite] states that COVID-19 pandemic and remote learning has caused a decrease in school bullying cases.
+The original paper (@citePaper) states that COVID-19 pandemic and remote learning has caused a decrease in school bullying cases.
 Our data has a slight different conclusion compared to the original paper (@fig-Composite-Search-Intensity-bully).
@@
 The unexpected rise in bullying during the pandemic could be attributed to various factors, for example, individuals seeking to alleviate stress through harmful behavior to other people.
-Furthermore, a disturbing trend of Chinese-hate emerged during this period, due to the misguided assumptions that China was responsible for spreading the virus [@citeChineseHate].
+Furthermore, a disturbing trend of Chinese-hate emerged during this period, due to the misguided assumptions that China was responsible for spreading the virus (@citeChineseHate).
 Asian students, especially Chinese ethnicity, might experience discriminatory actions, verbal abuse, or physical assaults due to this misinformation.
@@
 Surprisingly, the shift to remote learning during the COVID-19 pandemic did not lead to an expected increase in cyberbullying cases.
-Given that students spent the majority of their time on digital devices [@citeDigitalDevices], it was natural to assume that cyberbullying would increase.
+Given that students spent the majority of their time on digital devices (@citeDigitalDevices), it was natural to assume that cyberbullying would increase.
 Instead, there was a noticeable decrease.
@@
 The reduction in personal interactions during remote learning may have played a role in diminishing students' motivations or reasons to engage in cyberbullying.
-Also, since students stayed at home, there would always be adult supervision, for students under 12 years old [@citeStudent], which may have regulated their behaviour.
+Also, since students stayed at home, there would always be adult supervision, for students under 12 years old (@citeStudent), which may have regulated their behaviour.
 This indicates that face-to-face interactions and the environmental factors have a strong impact on the prevalence of online harassment.
@@
 The local trough occurs during the summer vacation when students are away from school.
-It can be inferred that there might be a positive correlation between academic stress and bullying and between in-person interactions and bullying [@citeCorrelation].
+It can be inferred that there might be a positive correlation between academic stress and bullying and between in-person interactions and bullying (@citeCorrelation).
 
 As the semester begins, students need to transition from a relaxed vacation state to a rigorous school learning state.
-As they navigate the challenges of academic demands, they may experience stress and peer pressure from many sources [@citePressure].
+As they navigate the challenges of academic demands, they may experience stress and peer pressure from many sources (@citePressure).
 This will urge students to release their emotions and stress by bullying other students.
@@
 This reduction in direct, in-person interactions tends to reduce social pressures.
-Some individuals may feel the need to show dominance within the school by performing bullying behaviors in the presence of others [@citeOthers].
+Some individuals may feel the need to show dominance within the school by performing bullying behaviors in the presence of others (@citeOthers).
 However, during vacations, the reduced personal interaction may reduce their need for such assertive actions, resulting in a decrease in bullying activities.

### 2024-02-15 outputs/paper/paper.qmd
finished result

--- 2024-02-15 outputs/paper/paper.qmd
@@
 # Results
+```{r}
+#| label: tbl-Search-Intensity
+#| tbl-cap:  Table-of-Search-Intensity by School Bullying and Cyber Bullying
+#| warning: false
+#| message: false
+#| echo: false
+knitr::kable(head(bully_clean_data),'markdown',col.names = c("US State", "Date", "Number of Searches", "Bully Type"),align = 'c',
+
+                      caption = "Sample Table for Search Intensity by School Bullying and Cyber Bullying (2012-2021)")
+```
 
 ```{r}
-#| label: fig-Composite-Search-Intensity 
-#| fig-cap: Composite-Search-Intensity both type
+#| label: fig-Composite-Search-Intensity-bully
+#| fig-cap: Composite-Search-Intensity by School Bullying and Cyber Bullying
 #| warning: false
@@
   geom_line() +
-  ggtitle("Composite Search Intensity for School Bullying and Cyberbullying") +
   xlab("Date") +
   ylab("Search Intensity") +
+   labs(title = "Composite-Search-Intensity by School and Cyber Bullying")+
   geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
 ```
@@
   geom_line() +
-  ggtitle("Composite Search Intensity for School Bullying") +
   xlab("Date") +
   ylab("Search Intensity") +
+   labs(title = "Composite-Search-Intensity by School Bullying")+
   geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
@@
   geom_line() +
-  ggtitle("Composite Search Intensity forCyberbullying") +
   xlab("Date") +
   ylab("Search Intensity") +
+     labs(title = "Composite-Search-Intensity by Cyber Bullying")+
   geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
@@
 
- The data presented in @fig-Composite-Search-Intensity provides valuable insights into the trends of searches from 2012 to 2021.
+The dataset represented by the table labeled @tbl-Search-Intensity furnishes a comprehensive overview of the cumulative number of searches related to bullying over the specified time frame.
+This table is a valuable resource for conducting a nuanced analysis, as it delineates key variables crucial for understanding the extent of harm experienced by individuals affected by bullying.
+The primary variables include time, state, the total number of searches, and the categorization of bullying incidents.
+The categorization of bullying incidents into different categories provides a nuanced understanding of the multifaceted nature of bullying.
+By disaggregating searches based on bullying categories, such as traditional bullying and cyberbullying, analysts can discern which forms of bullying are more prevalent or garner more attention during specific time periods and in particular states.
+
+In essence, the @tbl-Search-Intensity table serves as a rich repository of information, offering a multifaceted perspective on the harm suffered by individuals affected by bullying.
+Researchers can leverage this dataset to uncover temporal trends, regional variations, and category-specific nuances, ultimately contributing to a more comprehensive and targeted approach in addressing the complex issue of bullying.
+
+The data presented in @fig-Composite-Search-Intensity-bully provides valuable insights into the trends of searches from 2012 to 2021.
 The observed pattern, with peaks of bullying during the first month of school and troughs in the summer, suggests a recurring seasonal variation in the interest or concern about bullying .
@@
 Additionally, understanding the lasting impact of these changes on bullying awareness and intervention efforts is crucial for developing effective strategies to address this issue in evolving educational landscapes.
+
+The two-dimensional analysis of bullying searches, as depicted in @fig-Number-of-Searches-represented-by-point-size, offers valuable insights into the regional variations and the overall prevalence of bullying concerns.
+By juxtaposing the number of bullying searches in specific states with the nationwide search volume, a nuanced understanding of the relative intensity of bullying-related issues emerges.
+The substantial discrepancy between the search volumes for bullying in New York State and New Jersey, with New York registering nearly twice the number of searches, underscores the regional disparities in the perception or awareness of bullying.
+This contrast could be influenced by a myriad of factors, such as differences in population density, educational policies, cultural dynamics, or varying levels of community engagement in anti-bullying initiatives.
+The elevated search volume in New York may suggest a higher incidence of bullying incidents or a greater public awareness and sensitivity to the issue.
+This heightened attention could be attributed to proactive anti-bullying campaigns, robust educational programs, or a more open dialogue surrounding the topic within the state.
+Conversely, the comparatively lower search volume in New Jersey may indicate a different set of contextual factors influencing the perception and reporting of bullying.
+The two-dimensional analysis not only provides insights into state-level variations but also allows for a comparison with the nationwide search volume.
+Understanding how specific states compare to the national average in terms of bullying searches can highlight regions where the issue is particularly salient or, conversely, where it may be relatively underreported or less prevalent.
+The two-dimensional analysis of bullying searches based on the number of state and nationwide searches reveals a nuanced landscape of regional variations in the perception and awareness of bullying.
+The disparities observed in Figure 4 provide a starting point for further investigations and interventions to address the complex and multifaceted nature of bullying at both the state and national levels.
 

### 2024-02-15 outputs/paper/paper.qmd
change ref

--- 2024-02-15 outputs/paper/paper.qmd
@@
 ## Data Measurements
-The measurement of bullying from Google Trends is the search intensity of keywords, which are published every month [@citePaper].
+The measurement of bullying from Google Trends is the search intensity of keywords, which are published every month (@citePaper).
 Search intensity stands for the fraction of a given area’s Google searches for a specific topic.
@@
 The original dataset contained 5 variables, which are named as “dma_json_code”, “date”, “keyword”, “hits”, and “ratio”.
-1. dma_json_code: the states of the United States
-2. date: the first day of every month from 2012. 01 to 2021. 02
+
+1. dma_json_code: the states of the United States.
+
+2. date: the first day of every month from January 2012 to February 2021.
+
 3. keyword: specific words that the people search on Google Trends that relate to bullying.
+
 4. hits: number of searchers of keywords in each month.
-5. ratio:
+
+5. ratio: ratio of the search intensity in Google Trend.
 
@@
 The original paper (@citePaper) states that COVID-19 pandemic and remote learning has caused a decrease in school bullying cases.
-Our data has a slight different conclusion compared to the original paper (@fig-Composite-Search-Intensity-bully).
+Our data has a slight different conclusion compared to the original paper (@fig-Composite-Search-Intensity-bully, @fig-Composite-Search-Intensity-sch, @fig-Composite-Search-Intensity-cyber).
 It is observed that with the sudden COVID-19 outbreak in the United States around January 2020, instances of school bullying experienced a notable surge, almost reaching global maxima in February 2020.

### 2024-02-15 outputs/paper/paper.qmd

@@
 
+Talk way more about it.
+
+# Results
+```{r}
+#| label: tbl-Search-Intensity
+#| tbl-cap:  Table-of-Search-Intensity by School Bullying and Cyber Bullying
+#| warning: false
+#| message: false
+#| echo: false
+knitr::kable(head(bully_clean_data),'markdown',col.names = c("US State", "Date", "Number of Searches", "Bully Type"),align = 'c',
+
+                      caption = "Sample Table for Search Intensity by School Bullying and Cyber Bullying (2012-2021)")
+```
+=======
 # Results {#sec-result}
@@
   ylab("Search Intensity") +
+   labs(title = "Composite-Search-Intensity by School and Cyber Bullying")+
   geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
@@
 ```{r}
-#| label: fig-Composite-Search-Intensity-sch
-#| fig-cap: Composite-Search-Intensity by School Bullying
+#| label: fig-Composite-Search-Intensity-school
+#| fig-cap: Composite-Search-Intensity school type
 #| warning: false
@@
   ylab("Search Intensity") +
+   labs(title = "Composite-Search-Intensity by School Bullying")+
   geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
@@
 #| echo: false
-
 # plot from "cyberbullying" data
@@
   ylab("Search Intensity") +
+     labs(title = "Composite-Search-Intensity by Cyber Bullying")+
   geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
@@
 ```
+
+The dataset represented by the table labeled @tbl-Search-Intensity furnishes a comprehensive overview of the cumulative number of searches related to bullying over the specified time frame.
+This table is a valuable resource for conducting a nuanced analysis, as it delineates key variables crucial for understanding the extent of harm experienced by individuals affected by bullying.
+The primary variables include time, state, the total number of searches, and the categorization of bullying incidents.
+The categorization of bullying incidents into different categories provides a nuanced understanding of the multifaceted nature of bullying.
+By disaggregating searches based on bullying categories, such as traditional bullying and cyberbullying, analysts can discern which forms of bullying are more prevalent or garner more attention during specific time periods and in particular states.
+
+In essence, the @tbl-Search-Intensity table serves as a rich repository of information, offering a multifaceted perspective on the harm suffered by individuals affected by bullying.
+Researchers can leverage this dataset to uncover temporal trends, regional variations, and category-specific nuances, ultimately contributing to a more comprehensive and targeted approach in addressing the complex issue of bullying.
 

### 2024-02-15 outputs/paper/paper.qmd
add estimand

@@
 These results provide insights into how schools can reduce bullying in a post-pandemic world and highlight a possible mechanism by which COVID-19 may have a differential impact on broader mental health.
+In this paper, we are interested in the bullying situation due to COVID-19 impact.
+However, the true effect might be hard to gather, since it is impossible to count every bullying incident.
+Therefore, the estimand of this study is search intensity of keywords that are related to bullying from Google Trends.
+This estimand can be a good representation of the bullying situation in each state.
 

### 2024-02-15 outputs/paper/paper.qmd
add link

--- 2024-02-15 outputs/paper/paper.qmd
@@
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: LINK."
+  - Mary Cheng
+  - Shipeng Zhang
+  - Yimiao Yuan
+thanks: "Code and data are available at: https://github.com/zero616/Covid-19-Analaysis.git."
 date: today

### 2024-02-15 outputs/paper/paper.qmd
add title

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "COVID-19 Pandemic Influence on K1-12 Student Bullying Situation"
 author: 
@@
 
+The two-dimensional analysis of bullying searches, as depicted in @fig-Number-of-Searches-represented-by-point-size, offers valuable insights into the regional variations and the overall prevalence of bullying concerns.
+By juxtaposing the number of bullying searches in specific states with the nationwide search volume, a nuanced understanding of the relative intensity of bullying-related issues emerges.
+The substantial discrepancy between the search volumes for bullying in New York State and New Jersey, with New York registering nearly twice the number of searches, underscores the regional disparities in the perception or awareness of bullying.
+This contrast could be influenced by a myriad of factors, such as differences in population density, educational policies, cultural dynamics, or varying levels of community engagement in anti-bullying initiatives.
+The elevated search volume in New York may suggest a higher incidence of bullying incidents or a greater public awareness and sensitivity to the issue.
+This heightened attention could be attributed to proactive anti-bullying campaigns, robust educational programs, or a more open dialogue surrounding the topic within the state.
+Conversely, the comparatively lower search volume in New Jersey may indicate a different set of contextual factors influencing the perception and reporting of bullying.
+The two-dimensional analysis not only provides insights into state-level variations but also allows for a comparison with the nationwide search volume.
+Understanding how specific states compare to the national average in terms of bullying searches can highlight regions where the issue is particularly salient or, conversely, where it may be relatively underreported or less prevalent.
+The two-dimensional analysis of bullying searches based on the number of state and nationwide searches reveals a nuanced landscape of regional variations in the perception and awareness of bullying.
+The disparities observed in Figure 4 provide a starting point for further investigations and interventions to address the complex and multifaceted nature of bullying at both the state and national levels.
+
 \newpage

### 2024-02-15 outputs/paper/paper.qmd
editing

--- 2024-02-15 outputs/paper/paper.qmd
@@
 author: 
-  - Mary Cheng
-  - Shipeng Zhang
-  - Yimiao Yuan
-thanks: "Code and data are available at: https://github.com/zero616/Covid-19-Analaysis.git."
+  - First author
+  - Another author
+thanks: "Code and data are available at: LINK."
 date: today
@@
 Additionally, understanding the lasting impact of these changes on bullying awareness and intervention efforts is crucial for developing effective strategies to address this issue in evolving educational landscapes.
+
+The two-dimensional analysis of bullying searches, as depicted in @fig-Number-of-Searches-represented-by-point-size, offers some insights into the regional variations and the overall prevalence of bullying concerns.
+By juxtaposing the number of bullying searches in specific states with the nationwide search volume, a nuanced understanding of the relative intensity of bullying-related issues emerges.
+The substantial discrepancy between the search volumes for bullying in New York State and New Jersey, with New York registering nearly twice the number of searches.
+The two-dimensional analysis not only provides insights into state-level variations but also allows for a comparison with the nationwide search volume.
+The two-dimensional analysis of bullying searches based on the number of state and nationwide searches reveals a nuanced landscape of regional variations in the perception and awareness of bullying.
 

### 2024-02-15 outputs/paper/paper.qmd
add test and abstract

--- 2024-02-15 outputs/paper/paper.qmd
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Each year in the United States, about one in five teens is bullied at school.
+When COVID-19 interferes with in-person interactions, we use Internet search data from Google Trend to track bullying patterns.
+We found a downward trend in searches about bullying and cyberbullying in schools as schools shift to online learning in the spring of 2020.
+This finding debunks the idea that cyberbullying increases as students become more exposed to technology, explaining the impact of epidemics on student mental health and providing ideas for future responses to cyber and school bullying."
 format: pdf
@@
 
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-## Diagnostics
-
-\newpage
-
 # References

### 2024-02-15 scripts/03-test_data.R

@@ -1,15 +1,41 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Tests the cleaned data and see if it is what we expected
+# Author: Mary Cheng, Yimiao Yuan, Shipeng Zhang
+# Date: 15 February 2024
+# Contact: yimiaomail@gmail.com, maryc.cheng@mail.utoronto.ca
+# License: --
+# Pre-requisites: run 01-download_data.R 02-data_cleaning.R first to get the cleaned dataset
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
-#### Test data ####
+#### Read Data ####
+file_path <- "../../outputs/data/bully_clean_data.csv"
+bully_clean_data <- read.csv(file_path)
+#### Test Data ####
+
+
+# Check that num_of_searches are all numeric
+bully_clean_data$num_of_searches |>
+  class() == "numeric"
+
+# Check that there are only three states in "us_state"
+bully_clean_data$us_state |>
+  unique() |>
+  length() == 3
+
+# Check that there are only three bully types in "bully_type"
+bully_clean_data$bully_type |>
+  unique() |>
+  length() == 3
+
+# Check that "num_of_searches" is no larger than 100 and no smaller than 0
+bully_clean_data$num_of_searches |>
+  max() <= 100
+bully_clean_data$num_of_searches |>
+  min() >= 0
+
+# Check that class of "date" are all dates
+bully_clean_data$date |>
+  class() == "Date"

### 2024-02-15 outputs/paper/Covid_19_Analysis.qmd
currect virsion

--- 2024-02-15 outputs/paper/paper.qmd
@@
 When COVID-19 interferes with in-person interactions, we use Internet search data from Google Trend to track bullying patterns.
-We found a downward trend in searches about bullying and cyberbullying in schools as schools shift to online learning in the spring of 2020.
+We found an overall downward trend in searches about bullying and cyberbullying in schools as schools shift to online learning in the spring of 2020.
 This finding debunks the idea that cyberbullying increases as students become more exposed to technology, explaining the impact of epidemics on student mental health and providing ideas for future responses to cyber and school bullying."
@@
 
+\newpage
 # Results {#sec-result}
+```{r}
+#| label: tbl-Search-Intensity
+#| tbl-cap:  Table-of-Search-Intensity by School Bullying and Cyber Bullying
+#| warning: false
+#| message: false
+#| echo: false
+knitr::kable(head(bully_clean_data),'markdown',col.names = c("US State", "Date", "Number of Searches", "Bully Type"),align = 'c',
+
+                      caption = "Sample Table for Search Intensity by School Bullying and Cyber Bullying (2012-2021)")
+```
 

### 2024-02-15 outputs/paper/Covid_19_Analysis.qmd
push

@@
 
-The two-dimensional analysis of bullying searches, as depicted in @fig-Number-of-Searches-represented-by-point-size, offers valuable insights into the regional variations and the overall prevalence of bullying concerns.
-By juxtaposing the number of bullying searches in specific states with the nationwide search volume, a nuanced understanding of the relative intensity of bullying-related issues emerges.
-The substantial discrepancy between the search volumes for bullying in New York State and New Jersey, with New York registering nearly twice the number of searches, underscores the regional disparities in the perception or awareness of bullying.
-This contrast could be influenced by a myriad of factors, such as differences in population density, educational policies, cultural dynamics, or varying levels of community engagement in anti-bullying initiatives.
-The elevated search volume in New York may suggest a higher incidence of bullying incidents or a greater public awareness and sensitivity to the issue.
-This heightened attention could be attributed to proactive anti-bullying campaigns, robust educational programs, or a more open dialogue surrounding the topic within the state.
-Conversely, the comparatively lower search volume in New Jersey may indicate a different set of contextual factors influencing the perception and reporting of bullying.
-The two-dimensional analysis not only provides insights into state-level variations but also allows for a comparison with the nationwide search volume.
-Understanding how specific states compare to the national average in terms of bullying searches can highlight regions where the issue is particularly salient or, conversely, where it may be relatively underreported or less prevalent.
-The two-dimensional analysis of bullying searches based on the number of state and nationwide searches reveals a nuanced landscape of regional variations in the perception and awareness of bullying.
-The disparities observed in Figure 4 provide a starting point for further investigations and interventions to address the complex and multifaceted nature of bullying at both the state and national levels.
-
 \newpage

### 2024-02-15 outputs/paper/Covid_19_Analysis.qmd
add

@@
   - Yimiao Yuan
-thanks: "Code and data are available at: https://github.com/zero616/Covid-19-Analaysis.git."
+thanks: "Code and data are available at: https://github.com/zero616/Covid-19-Analaysis.git. DOI of replication is at:http://dx.doi.org/10.1257/aeri.20210456"
 date: today

### 2024-02-15 outputs/paper/Covid_19_Analysis.qmd
add

@@
 Some data cleaning is performed, such as renaming column names, filtering and mutating the column, etc.
-The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `dplyr` (@citeDplyr), `ggplot2` (@citeGgplot2).
+The cleaned data will be analyzed and performed using R (@citeR) with `tidyverse` (@citeTidyverse), `dplyr` (@citeDplyr), `ggplot2` (@citeGgplot2),`knitr`(@R-knitr),`janitor`(@R-janitor).
 
@@
 #| label: tbl-Search-Intensity
-#| tbl-cap:  Table-of-Search-Intensity by School Bullying and Cyber Bullying
+#| tbl-cap:  Sample Table for Search Intensity by School Bullying and Cyber Bullying (2012-2021)
 #| warning: false
@@
 #| echo: false
-knitr::kable(head(bully_clean_data),'markdown',col.names = c("US State", "Date", "Number of Searches", "Bully Type"),align = 'c',
-
-                      caption = "Sample Table for Search Intensity by School Bullying and Cyber Bullying (2012-2021)")
+knitr::kable(head(bully_clean_data),'markdown',col.names = c("US State", "Date", "Number of Searches", "Bully Type"),align = 'c')
 ```
@@
 Future research should focus on gathering more inclusive and representative data by increasing the volume of data entries and mitigating bias in data collection. 
-Beyond simply collecting data about bullying, researchers should investigate the mental well-being of students affected by bullying.By investigating their mental well-being, researchers can arrive at conclusions if the mental health support system is effective for students in the school.
+Beyond simply collecting data about bullying, researchers should investigate the mental well-being of students affected by bullying.
+By investigating their mental well-being, researchers can arrive at conclusions if the mental health support system is effective for students in the school.
 It is important to ensure that individuals who experience bullying have access to the necessary resources and support.
